Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
pass over intro

Maintenance includes not only adaptation to changes in new proof assistant versions, but also reorganization to ease future maintenance effort and accommodate new contributions. Documentation is usually two-fold: \emph{source code comments} that describe specific definitions and results in-line and \emph{books} that carefully introduce the library and its idioms~\cite{MCB,TheoremProvingLean4}. The former tends to be terse and dense and serves experienced users, while the latter is more long-winded and exhaustive and serves beginners. As a library changes and expands, all its documentation needs to be made consistent and complete. Authors use a wide range of techniques, including literate programming~\cite{Knuth1984} and custom tools, to pretty-print and check source code snippets and generate proof assistant output.

While books that document proof assistant libraries are valuable to beginners, the purpose of recently published books is mainly instrumental, i.e., to teach a certain topic or technique. We believe that books can instead become \emph{ends in themselves}---not just sources of learning, but also sources of inspiration and entertainment.

>>>>

Maintenance includes not only adaptation to changes in new proof assistant versions, but also reorganization to accommodate new contributions. Documentation is usually two-fold: \emph{source code comments} that describe specific definitions and results in-line and \emph{books} that carefully introduce the library and its idioms~\cite{MCB,TheoremProvingLean4}. The former tends to be terse and dense and serves experienced users, while the latter is more long-winded and exhaustive and serves beginners. As a library changes and expands, all its documentation needs to be made consistent and complete. Authors use many techniques, including literate programming~\cite{Knuth1984} and custom tools, to pretty-print and check source code snippets and generate proof assistant output.

While books that document proof assistant libraries are valuable to beginners, the purpose of recently published books is mainly instrumental, i.e., to teach a certain topic or technique. We believe that books and libraries can instead become \emph{ends in themselves}---not just sources of exposition and learning, but also sources of inspiration and entertainment.
